Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-07 draft/paper1_v11.tex
Simulations of ICL

    At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
    galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
    Although the rising stellar velocity dispersion in the outskirt of massive BCG
    has been used as evidence of a kinematically separated ICL component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
    we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
    an integrated component. 
    They both carry important information regarding the assembly of central galaxy 
    and its dark matter halo.

>>>>

    At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
    galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
    Although the rising stellar velocity dispersion in the outskirt of massive BCG
    has been used as evidence of a kinematically separated ICL component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
    we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
    an integrated component. 
    They both carry important information regarding the assembly of central galaxy 
    and its dark matter halo. 
    In recent years, we can start to investigate the origin and evolution of ICL using 
    simulations where physical separation of ICL is possible
    (e.g. \citealt{SommerLarsen2005, Murante2007, Martel2012, Cui2014, Cooper2015, 
    Harris2017}). 
    It will be interesting to perform detailed comparisons between these simulations 
    and deep HSC observations to look into the contributions from different stellar 
    components to the halo of massive galaxy.
